Distributional State Aggregation

### 2020-03-02 minutia/paper/paper.tex
MacRep IQR still in progress

>>>>

    We use a randomized policy to simulate trajectories and collect samples to attenuate bias in action selection
    process.
    As it has shown the literature, $\epsilon$-greedy has a bias in solving exploration-exploitation dilemma, we
    explore the environment by following a randomized policy with a uniform distribution.
